Evolution of Flare Activity in GKM Stars Younger than 300 Myr over Five Years of TESS Observations

### 2024-04-30 src/tex/ms.tex
referee report edits

@@

%With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}. In order to model the
flare profile, we employ the analytical model developed by \cite{tovar22}. This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy
associated with each flare.

@@

This process provided a final sample of \nstars\ unique targets. These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67; Sector 67 was
the latest available sector at the time that this analysis was performed. In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions, ages and effective
temperatures, $T_\textrm{eff}$, of the final sample. Because many of the groups are located at or near the ecliptic poles, many of our targets were observed over multiple TESS
sectors. We use $T_\textrm{eff}$ as our stellar characterization metric over the standard $M_\star$ because $\sim 600$ stars in our sample lack mass information in the TIC.
The entirety of the available data yielded 17,964 light curves processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16}. Our sample has an average
of $\sim 3$ light curves per target (although with significant spread across targets). For our analysis, we used the SPOC-processed SAP\_FLUX.

@@

Once we downloaded the light curves for each target, we performed the following procedure to identify stellar flares. First, we implemented the machine learning flare-identification
methods presented and described in \cite{feinstein20}. This method relies on the similar time-dependent morphologies of all flare events. These flare-profiles can generally be
described as a sharp rise followed by an exponential decay in the white light curve. This identification-technique implements the convolutional neural network (CNN) \texttt{stella}
\citep{feinstein20}. The CNN  was trained on  a   by-eye validated catalogue of flares from TESS Sectors 1 and 2 with 2-minute data \citep{guenther19_flares}.

@@

Based on these advantages, the final compiled sample of flares is unbiased towards low-amplitude/low-energy flares. It is important to note that these low-energy events are typically
not identified in traditional sigma-outlier identification
methods \citep{chang15}. The \texttt{stella} CNN models calculate the probability that a data point in a light curve is associated with a flaring event. Specifically, it takes the light
curve (time, flux, flux error) as an input and returns an array with values of [0,1], which are treated as the probability a data point is (1) or is not (0) part of a flare. We ran every
light curve through 10 independent \texttt{stella} models and averaged the outputs to ensure that our statistics were accurate. We note that in this processing, the CNN ignores 200-minutes
before and after any gaps in the data. Therefore, any flares which occur during these times are not identified.

@@

The analytic model robustly  accounts for physically-motivated flare features. Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale, (iii) rapid cooling phase
timescale, and (iv) slow cooling phase timescale. We implemented a nonlinear least squares optimization to fit the flare peak time ($t_\textrm{peak}$), full width at half maximum (FWHM),
and the amplitude ($A$) of each flare in the sample.  We combine the model with a second-order polynomial fit to a 1.2-hour baseline before and after the flare  during only the fitting stage.
This was implemented in order to account for any slope due to rotational modulation, and therefore was particularly relevant for the rapid rotators ($P_\textrm{rot} < 2$~days).

@@

@@

\begin{equation}\label{eq:fr}
  \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)\,.
\end{equation}
In Equation (\ref{eq:fr}), $\mathcal{R}$ is the flare rate in units of day$^{-1}$, $t_\textrm{obs}$ is the total amount of time a target was observed with TESS, and $p_i$ is the probability
that flare $i$ is a true flare as assigned by \texttt{stella}. We compare the calculated $R_0$ to measured flare rates for all stars with measured $P_\textrm{rot}$. The results are presented
in Figure~\ref{fig:prot_histograms}.

@@

\begin{equation}\label{eq:dpda}
  dp/dA \propto A^{-\alpha_T} e^{-A/A_*}\,.
\end{equation}
In Equation (\ref{eq:dpda}),  $A$ is the amplitude of the flare, $A_*$ is a flare amplitude cutoff parameter and $\alpha_T$ is the slope, rather than $\alpha$. We fit the slopes using the
MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}. We used the log-likelihood function in \cite{seligman22} and  fit for $A_*$ and $\alpha_T$. We initialized the MCMC fit
with 200 walkers and evaluated the fit over 5000 steps. The first 1000 steps were discarded upon visual inspection. The results are presented in Figure~\ref{fig:truncated}.

@@

The Sun undergoes an 11-year solar cycle during  which it oscillates between high and low magnetic activity. This magnetic cycle manifests  in a variety of observables. One of the primary
indicators of the solar cycle is a stark change in the flare rate; this rate can vary by more than an order of magnitude between Solar maxima and minima \citep{webb94}. However, it is worth
noting that other, shorter periodicities have been observed in Solar flares \citep{}. Moreover, energetics of the flares that are produced on the solar surface vary dramatically over the
course of the solar cycle \citep{Bai1987,Bai2003}. Direct and indirect evidence  of the solar cycle have also been observed in radio flux, total solar irradiance, the magnitude and geometry
of the magnetic field, coronal mass ejections affiliated with flares, geomagnetic activity, cosmic ray fluxes and radioisotopes in ice cores and tree rings. For a recent review, see \citet{Hathaway2015}.

While other stars should also experience activity cycles like the Sun, they are more difficult to measure. Constraints on stellar cycles have predominantly relied on long baseline variations
in stellar photometry \citep[see recent reviews by ][]{jeffers23, isik23}, typically observed at cadences which cannot resolve stellar flares. However,  tracing stellar cycles via stellar
flares may be more reliable, as flares are a direct consequence of magnetic activity. \cite{} explored measuring the stellar cycle length of KIC 8507979, a star in the \textit{Kepler} field
which was observed for 18 90-day quarters. \cite{scoggins19} found the flare rate decreased over each quarter, which could be fit by
$L_\textrm{fl}/L_\textrm{Kp} = (-9.96 \pm 3.94) \times 10^{-2} \times t_\textrm{yr} + (2.43 \pm 0.11)$, where $t_\textrm{yr}$ is the time in years, and $L_\textrm{fl}/L_\textrm{Kp}$ is a
parameterization of the \textit{Kepler} flare rate \citep{lurie15}.

%It is possible that the length of the stellar cycle is related to the rotational period $P_\textrm{rot}$ or the Rossby number $R_0$ of the star as ... \citep{}. If this is the case,
then stars with $P_\textrm{rot}$ will have shorter stellar cycle lengths.

@@

Here, we explore observables from solar flares between 2002 and 2018 in the Reuven Ramaty High Energy Solar Spectroscopic Imager \citep[RHESSI;][]{lin02} flare
catalog.\footnote{\url{https://hesperia.gsfc.nasa.gov/rhessi3/data-access/rhessi-data/flare-list/index.html}} The RHESSI mission observes the Sun in the hard X-ray
(HXR; $> 25$~keV) and has detected over $100,000$ solar flares in 16 years of operations. These observations covered the second half of solar Cycle 23 and the beginning of
solar Cycle 24. We use the publicly available RHESSI flare catalog to determine  metrics that would be most useful when searching for evidence of stellar cycles. One potential
issue with this analysis is that the HXR observations from RHESSI and white-light observations from TESS may not be directly correlated. However, there is a close spatial and
temporal correspondence between HXR and white-light flares on the Sun \citep{fletcher07, krucker11, kleint16}. Therefore, the HXR solar flares with energies between $25 - 50$~keV
are likely representative of solar white-light flares, and are a comparable sample to our TESS sample. First, the total number of flares detected in the $25 - 50$~keV bandpass
varied by 650~flares from solar maximum in 2002 to solar minimum in 2008. This variation correlates to a change in flare rate from $1.81$ to $0.02$ flares day$^{-1}$ on average.
Second, the flare frequency distribution changes between solar minimum and maximum because the frequency of the highest-energy flares decreases.  Finally, the total flare luminosity
relative to the total luminosity correlates with the stellar cycle. This is defined by \cite{lurie15} as

@@

It is not clear what the length of the activity cycles are for stars other than the Sun. For this order of magnitude estimate we therefore assume that the activity cycles of all stars in our
sample are similar to that of the Sun. This approximation is valid   if the length of stellar cycles on average is not more than an order of magnitude different than that of the sun. By
observing $N\sim$108 stars for a $\tau\sim$5 year baseline, assuming that each has a $P\sim10$ year activity cycle, we would expect that during that time period $\tau /P N\sim50$ stars should
experience a peak in their stellar cycle during the observations. Moreover, our analysis will only be sensitive to activity cycles if there is not only a peak, but also lower activity in the
year before and after the peak. Therefore, the number of stars that we would expect to identify that have a peak in year 2 should be $\tau /P N /3\sim16$. Therefore we would expect to identify
$\sim16$ stars exhibiting a peak in their activity cycle during these observations, which is  similar to what we have found. However, it is likely that there is a variety of lengths of stellar
cycles in our population and the exact correspondence between the number found and the number estimated is simply a manifestation of the crude order of magnitude approximation that we employed
rather than an exact correspondence. Nevertheless, this represents  tentative detections of peaks in stellar activity cycles and that on average the length of these cycles is not an order of
magnitude different than that of the Sun.

@@

We thank David Wilson for thoughtful insights and useful conversations. This work made use of the open-source package, \textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes reproducible publications. ADF acknowledges funding from NASA through the NASA Hubble Fellowship grant HST-HF2-51530.001-A awarded by STScI. DZS is supported by an NSF Astronomy and Astrophysics Postdoctoral Fellowship under award AST-2202135. This research award is partially funded by a generous gift of Charles Simonyi to the NSF Division of Astronomical Sciences.  The award is made in recognition of significant contributions to Rubin Observatory’s Legacy Survey of Space and Time.

>>>>

\textcolor{red}{This paper was written using the \textit{showyourwork!} open-source
software package. The objective of \textit{showyourwork!} is to improve reproducibility
and transparency of scientific research by compiling the manuscript and figures
simultaneously. All of the data in this work is hosted on GitHub\footnote{The GitHub is
hyperlinked in the \textit{showyourwork!} stamp at the top of the first page of this manuscript,
 and can also be found here: \url{https://github.com/afeinstein20/young-stellar-flares}.} and
 Zenodo.\footnote{} At the end of every caption figure in this manuscript, there is a GitHub icon
 (\faGithub), which links to the Python script used to create that figure.}

@@

@@

This process provided a final sample of \nstars\ unique targets. These targets
have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67;
Sector 67 was the latest available sector at the time that this analysis was performed.
In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions, ages
and effective temperatures, $T_\textrm{eff}$, of the final sample. Because many of
the groups are located at or near the ecliptic poles, many of our targets were observed
over multiple TESS sectors. We use $T_\textrm{eff}$ as our stellar characterization
metric over the standard $M_\star$ because $\sim 600$ stars in our sample lack mass
information in the TIC. The entirety of the available data yielded 17,964 light curves
processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16},
\textcolor{red}{which can be accessed on MAST under DOI  \href{http://dx.doi.org/10.17909/t9-nmc8-f686}{10.17909/t9-nmc8-f686}.}
Our sample has an average of $\sim 3$ light curves per target (although with significant
spread across targets). \textcolor{red}{We downloaded all light curves using \texttt{lightkurve}\footnote{\url{https://doi.org/10.5281/zenodo.4654522}}.}
For our analysis, we used the SPOC-processed SAP\_FLUX.

@@

Once we downloaded the light curves for each target, we performed the following
procedure to identify stellar flares. We implemented the machine learning
flare-identification methods presented and described in \cite{feinstein20}.
This method relies on the similar time-dependent morphologies of all flare events.
These flare-profiles can generally be described as a sharp rise followed by an
exponential decay in the white light curve. This identification-technique implements
the convolutional neural network (CNN) \texttt{stella} \citep{feinstein20},
\textcolor{red}{although other architectures have been explored for flare identification
\citep[e.g.][]{vida18}.}  The CNN  was trained on a by-eye validated catalogue of flares
from TESS Sectors 1 and 2 with 2-minute data \citep{guenther19_flares}.

@@

Based on these advantages, the final compiled sample of flares is unbiased towards
low-amplitude/low-energy flares. It is important to note that these low-energy events
are typically not identified in traditional sigma-outlier identification
methods \textcolor{red}{\citep[e.g.][]{chang15, vasilyev22}}. \textcolor{red}{While
significant developments have been achieved to better model and detrend stellar
variability \citep[e.g.][]{bicz22}, these methods can be computationally intensive}
The \texttt{stella} CNN models calculate the probability that a data point in a light
curve is associated with a flaring event. Specifically, it takes the light curve (time,
flux, flux error) as an input and returns an array with values of [0,1], which are
treated as the probability a data point is (1) or is not (0) part of a flare. We ran
every light curve through 10 independent \texttt{stella} models and averaged the
outputs to ensure that our statistics were accurate. We note that in this processing,
the CNN ignores 200-minutes before and after any gaps in the data. Therefore, any
flares which occur during these times are not identified. \textcolor{red}{From by-eye
vetting of $\sim 300$ light curves, we found 2~flares within the first 200~minutes of
the orbital gaps. Therefore, we estimate $\leq 120$~flares are missed in our catalog.}

@@

The analytic model robustly  accounts for physically-motivated flare features.
Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale,
(iii) rapid cooling phase timescale, and (iv) slow cooling phase timescale. We
implemented a nonlinear least squares optimization to fit the flare peak time
($t_\textrm{peak}$), full width at half maximum (FWHM), and the amplitude ($A$)
of each flare in the sample. \textcolor{red}{We note that there are several other
physically-motivated flare models which could be used, such as those presented in
\cite{gryciuk17, pietras22, yang23_lp}; these models include using two profiles to
fit the impulsive and late phases of the flare.} We combine the model with a
second-order polynomial fit to a 1.2-hour baseline before and after the flare
during only the fitting stage. This was implemented in order to account for any
slope due to rotational modulation, and therefore was particularly relevant for the
rapid rotators ($P_\textrm{rot} < 2$~days).

@@

\subsubsection{\textcolor{red}{Comparison of Flare Models}}

\textcolor{red}{\cite{tovar22} demonstrated that the flare model works well for
flares with amplitudes $\geq 2$ (i.e. double the baseline flux). However, other
works such as \cite{pietras22} have demonstrated that a double-flare profile better
fits high energy flares. To quantify how well the Llamaradas Estelares model works,
we refit and calculate the $\chi^2$ for a subset of high amplitude flares ($A \geq 0.4$)
using Equation 3 in \cite{pietras22}, a double-peak flare model, which is:}

\begin{equation}\label{eqn:flare}
\begin{split}
    f(\tau) = \int_0^\tau\bigg( A_1\, \exp\bigg[\frac{-(t-B_1)^2}{C_1^2}\bigg] \,\exp\bigg[\frac{(t-\tau)}{D_1}\bigg]\\+A_2 \,\exp\bigg[\frac{-(t-B_2)^2}{C_2^2}\bigg] \,\exp\bigg[\frac{(t-\tau)}{D_2}\bigg]\bigg) \textrm{d}t
\end{split}
\end{equation}

\textcolor{red}{where $A$ is is related to amplitude of the flare, $B$ relates
to the total energy released during the flare, $C$ relates to the timescale of
the flare, $D$ is related to the decay timescale, $\tau$ is the time of a given
cadence, and $t$ is the time to integrate over. The subscripts 1 and 2 indicate
which flare variables are associated with the first and second flare profile. We
refit 900~high-amplitude flares following Equation~\ref{eqn:flare}. We plot the
results of this refitting in Figure~\ref{fig:model_fit}.}

\begin{figure}[ht!]
    \script{model_fit.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/model_fit.pdf}
        \caption{
            \textcolor{red}{Comparison fits between the Llamaradas Estelares
            single-peak model from \cite{tovar22} and the double-peak flare model
            from \cite{pietras22} for flares with $A \geq 0.4$. Top (A): Comparison
            in the $\chi^2$ between the best-fit model for 900 flares. A one-to-one
            line is plotted in peach to guide the eye. Across this sample of
            high-amplitude flares, there is good agreement between the fits for
            these two distinct models. Bottom: Comparison in best-fit models for
            a subset of flares. The best-fit Llamaradas Estelares model is plotted
            in blue; the best-fit double-peak model is plotted in orange. We
            highlight examples where the double-peak flare model has the better
            fit (B, C), the Llamaradas Estelares flare model has the better fit
            (D, E), and where the models perform equally as well (F, G). We note
            there is no correlation between flare amplitude and preferred model.}
        }
        \label{fig:model_fit}
    \end{centering}
\end{figure}

\textcolor{red}{Broadly, we find the flare model from \cite{tovar22} and \cite{pietras22}
to fit the majority of the high-amplitude flares equally as well (Figure~\ref{fig:model_fit}\,A).
We highlight several examples where one model fits better than the other in Figure~\ref{fig:model_fit}\,B-E,
and cases where both profiles fit the data equally as well Figure~\ref{fig:model_fit}\,F-G.
Flares which prefer the Llamaradas Estelares model tend to have a more accurately fit flare
amplitude. Flares which prefer the double-peak model tend to have an extended decay timescale,
which is better fit by the addition of a secondary flare. Flares which are fit equally well by
both models tend to have a better fit to the amplitude in the Llamaradas Estelares model, but a
better fit to the decay timescale in the double-peak flare model.}

@@

\begin{equation}\label{eq:fr}
  \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)\,.
\end{equation}

In Equation (\ref{eq:fr}), $\mathcal{R}$ is the flare rate in units of day$^{-1}$,
$t_\textrm{obs}$ is the total amount of time a target was observed with TESS, and
$p_i$ is the probability that flare $i$ is a true flare as assigned by \texttt{stella}.
We compare the calculated $R_0$ to measured flare rates for all stars with measured
$P_\textrm{rot}$. The results are presented in Figure~\ref{fig:prot_histograms}.

@@

\begin{equation}\label{eq:dpda}
  dp/dA \propto A^{-\alpha_T} e^{-A/A_*}\,.
\end{equation}

In Equation (\ref{eq:dpda}),  $A$ is the amplitude of the flare, $A_*$ is a flare
amplitude cutoff parameter and $\alpha_T$ is the slope, rather than $\alpha$. We fit
the slopes using the MCMC method implemented in \texttt{emcee} \citep{goodman10, emcee}.
We used the log-likelihood function in \cite{seligman22} and  fit for $A_*$ and $\alpha_T$.
We initialized the MCMC fit with 200 walkers and evaluated the fit over 5000 steps.
The first 1000 steps were discarded upon visual inspection. The results are presented
in Figure~\ref{fig:truncated}.

@@

The Sun undergoes an 11-year solar cycle during  which it oscillates between high and
low magnetic activity. This magnetic cycle manifests  in a variety of observables. One
of the primary indicators of the solar cycle is a stark change in the flare rate; this
rate can vary by more than an order of magnitude between Solar maxima and minima
\citep{webb94}. Moreover, energetics of the flares that are produced on the solar
surface vary dramatically over the course of the solar cycle \citep{Bai1987,Bai2003}.
Direct and indirect evidence  of the solar cycle have also been observed in radio flux,
total solar irradiance, the magnitude and geometry of the magnetic field, coronal
mass ejections affiliated with flares, geomagnetic activity, cosmic ray fluxes and
radioisotopes in ice cores and tree rings. For a recent review, see \citet{Hathaway2015}.

While other stars should also experience activity cycles like the Sun, they are
more difficult to measure. \textcolor{red}{Constraints on stellar cycles have
predominantly relied on long baseline variations in stellar photometry, typically
observed at cadences which cannot resolve stellar flares \citep[see recent reviews
by ][]{jeffers23, isik23}}. However,  tracing stellar cycles via stellar flares may
be more reliable, as flares are a direct consequence of magnetic activity. \cite{scoggins19}
explored measuring the stellar cycle length of KIC 8507979, a star in the \textit{Kepler}
field which was observed for 18 90-day quarters. \cite{scoggins19} found the flare rate
decreased over each quarter, which could be fit by
$L_\textrm{fl}/L_\textrm{Kp} = (-9.96 \pm 3.94) \times 10^{-2} \times t_\textrm{yr} + (2.43 \pm 0.11)$,
where $t_\textrm{yr}$ is the time in years, and $L_\textrm{fl}/L_\textrm{Kp}$ is
a parameterization of the \textit{Kepler} flare rate \citep{lurie15}.

@@

Here, we explore observables from solar flares between 2002 and 2018 in the Reuven
Ramaty High Energy Solar Spectroscopic Imager \citep[RHESSI;][]{lin02} flare
catalog.\footnote{\url{https://hesperia.gsfc.nasa.gov/rhessi3/data-access/rhessi-data/flare-list/index.html}}
\textcolor{red}{The RHESSI mission observes the Sun across a wide range of X-ray energies,
from 3 keV-17 MeV, with high temporal and energy resolutions as well as with high signal
sensitivity. Such a wide energy range enables the ability to explore both thermal and
non-thermal emission observed during flare events. Over 16 years of operations, over
$100,000$ solar flares have been observed and characterized in RHESSI data.} These
observations covered the second half of solar Cycle 23 and the beginning of Solar
Cycle 24. We use the publicly available RHESSI flare catalog to determine  metrics
that would be most useful when searching for evidence of stellar cycles. One potential
issue with this analysis is that the HXR observations from RHESSI and white-light
observations from TESS may not be directly correlated. However, there is a close spatial
and temporal correspondence between HXR and white-light flares on the Sun
\citep{fletcher07, krucker11, kleint16}. \textcolor{red}{In particular, \cite{namekata17}
demonstrated the difference spatially resolved flares as observed with RHESSI HXR and the
Solar Dynamics Observatory (SDO)/Helioseismic and Magnetic Imager (HMI) white-light. In
some examples, the HMI white-light emission is seen to last longer than the HXR,
indicating the white-light emission is related to non-thermal electrons.}

\textcolor{red}{However, other examples of simultaneous HXR and white-light flare
observations in \citep{namekata17} show similar flare durations. Therefore, we take
the HXR solar flares with energies between $25 - 50$~keV as likely representative
of solar white-light flares, and are a comparable sample to our TESS sample.} First,
the total number of flares detected in the $25 - 50$~keV bandpass varied by 650~flares
from solar maximum in 2002 to solar minimum in 2008. This variation correlates to
a change in flare rate from $1.81$ to $0.02$ flares day$^{-1}$ on average. Second,
the flare frequency distribution changes between solar minimum and maximum because
the frequency of the highest-energy flares decreases.  Finally, the total flare
luminosity relative to the total luminosity correlates with the stellar cycle.
This is defined by \cite{lurie15} as

@@

It is not clear what the length of the activity cycles are for stars other than
the Sun. For this order of magnitude estimate we therefore assume that the activity
cycles of all stars in our sample are similar to that of the Sun. This approximation
is valid   if the length of stellar cycles on average is not more than an order
of magnitude different than that of the sun. By observing $N\sim$108 stars for a
$\tau\sim$5 year baseline, assuming that each has a $P\sim10$ year activity cycle,
we would expect that during that time period $\tau /P N\sim50$ stars should
experience a peak in their stellar cycle during the observations. Moreover, our
analysis will only be sensitive to activity cycles if there is not only a peak,
but also lower activity in the year before and after the peak. Therefore, the
number of stars that we would expect to identify that have a peak in year 2 should
be $\tau /P N /3\sim16$. Therefore we would expect to identify $\sim16$ stars
exhibiting a peak in their activity cycle during these observations, which is
similar to what we have found.

However, it is likely that there is a variety of lengths of stellar cycles in our
population and the exact correspondence between the number found and the number
estimated is simply a manifestation of the crude order of magnitude approximation
that we employed rather than an exact correspondence. Nevertheless, this represents
tentative detections of peaks in stellar activity cycles and that on average the
length of these cycles is not an order of magnitude different than that of the Sun.

\textcolor{red}{The results presented here are consistent with those presented in
previous studies of magnetic activity cycles in young stars. \cite{olah16} analyzed
29 stars from the Mount Wilson survey which had $\sim 36$ years of \ion{Ca}{2}
H \& K monitoring. Roughly 16 stars in this sample have constrained ages of $< 1$~Gyr
via gyrochronology. This sample of stars have $P_\textrm{rot} = 18.1 \pm 12.2$~days
and magnetic activity cycles of $P_\textrm{cyc} = 7.6 \pm 4.9$~years. There is
significantly more dispersion in the young stellar cycle lengths than for the older
stars. \cite{olah16} concluded that young stars show more complex interannual variations
in magnetic activity. While stars age, magnetic braking will increase the rotation
of the star. Once this process has occurred, the magnetic activity cycle becomes more
well-behaved, as seen on the Sun.}

\textcolor{red}{We apply the relationship between $log(1/P_\textrm{rot})$ and 
$log(P_\textrm{cyc}/P_\textrm{rot})$ described in \cite{olah16} to estimate the
activity cycles in our sample. 10 of our 11 candidates have measured
$P_\textrm{rot} = 0.41 - 5.22$~days. Using the best-fit slope of $0.76 \pm 0.15$,
we estimate the $P_\textrm{cyc} = 0.81 - 1.49$~years. Strong evidence of shorter
activity cycles than $\sim 3$~years may be missed by the sparse annual sampling
from TESS. Redesigning the next TESS extended mission to stare at the northern and
southern ecliptic poles continuously for two years, instead of alternating poles,
may help resolve these shorter activity cycles, if present.}

@@

We thank David Wilson for thoughtful conversations. \textcolor{red}{We thank the anonymous reviewer for their insightful report,
which improved the clarity and quality of this manuscript.} This work made use of the open-source package,
\textcolor{red}{\textit{showyourwork!}} \citep{luger2021}, which promotes reproducible publications. ADF acknowledges funding from
NASA through the NASA Hubble Fellowship grant HST-HF2-51530.001-A awarded by STScI. DZS is supported by an NSF Astronomy and Astrophysics
Postdoctoral Fellowship under award AST-2202135. This research award is partially funded by a generous gift of Charles Simonyi to the NSF
Division of Astronomical Sciences. The award is made in recognition of significant contributions to Rubin Observatory’s Legacy Survey of Space and Time.
